method

### 2021-09-01 06_Paper/ER-ED/method.Rmd
added text

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED. 
"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]. 
A complete list of all measures assessed in the study can be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.

@@

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. 
The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
Furhter, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
An evolutionary algorithm () was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
A complete list of all pictures and their classification into sets can be found in supplementary material X.

>>>>

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED. 
According to the 21-word-solution, "We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]. 
A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
We will use all available data in subsequent analyses.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.

@@

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. 
The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
A complete list of all pictures and their classification into sets can be found in supplementary material X.
